% Results
\subsection{Insights Evaluation}

A comprehensive evaluation of generated insights was conducted through a complete test run involving the upload of a mock sales interview call. The audio recording was successfully processed using AssemblyAI’s Transcript API, accurately converting the conversation into structured textual data. This transcription was seamlessly displayed in the chat interface, enabling real-time visual confirmation.

The transcribed text was then forwarded to the ChatGPT model along with the activated system prompt specifically tailored for extracting sales insights. Additional contextual prompts were also included to enhance the relevance of AI responses. The returned AI-generated sales insights were subsequently evaluated for accuracy, relevance, and practical applicability.

The validation process confirmed that the insights generated effectively identified critical sales information, such as key pain points including ineffective Facebook ads, limited content creation resources, and concerns about costs and turnaround times. Additionally, the insights accurately captured the customer's stated goals of improving ad conversions, enhancing brand visibility, and streamlining content creation. The AI-generated sales proposal included a comprehensive package tailored precisely to these insights, recommending solutions such as high-resolution visuals, professional styling, and efficient processes.

This successful end-to-end validation demonstrates the robustness and efficacy of the implemented solution, affirming its capability to significantly enhance sales processes through intelligent automation and insightful analytics tailored specifically to customer needs and constraints.
